Efficient Simulation of Economic and Ecological Dynamics for Marine Spatial Planning

### 2022-10-10 marlin-paper.qmd
adding deep water snapper to coral reef example

@@

| State                 | Distribution          | Description                                     |
|-----------------------|-----------------------|-------------------------------------------------|
| $\sigma_{centroid}$   |                       | Standard deviation of habitat centroid          |
| $\sigma_{habitat}$    |                       | Standard deviation around centroid              |
| Spatial catchability  |                       | Catchability varies in space                    |
| Spatial allocation    |                       | Fleet allocation strategy                       |
| F/M                   |                       | Fishing mortality relative to natural mortality |
| Adult movement rate   |                       |                                                 |
| Recruit movement rate |                       |                                                 |
| Hyperallometry        |                       | Presence of hyperallometric fec                 |
| DD timing             |                       | Timing of density dependence                    |
| Seasonal Movement     | $\subset[TRUE,FALSE]$ | Seasonal Movement Present                       |

>>>>

<!-- Single column, double line spaced -->
<!-- Within the word count (no more than 7000-8000 words for Standard Articles, 3000-4000 words for Applications and Practical Tools) -->
<!-- Continuous line and page numbering throughout -->
<!-- Clearly defined manuscript structure as standard: Author details, Abstract (must be numbered 1-4 according to Manuscript Specifications), Keywords, Introduction, Materials and Methods, Results, Discussion, Figures and Tables with captions -->
<!-- Figures and Tables can be embedded within the text where referenced to facilitate reviewing -->
<!--         Author Contributions (if >1 author – see Authorship Policy). -->
<!--         Statement of where you intend to archive your data -->

@@

| State                 | Distribution          | Description                                     |
|------------------|------------------|------------------------------------|
| $\sigma_{centroid}$   |                       | Standard deviation of habitat centroid          |
| $\sigma_{habitat}$    |                       | Standard deviation around centroid              |
| Spatial catchability  |                       | Catchability varies in space                    |
| Spatial allocation    |                       | Fleet allocation strategy                       |
| F/M                   |                       | Fishing mortality relative to natural mortality |
| Adult movement rate   |                       |                                                 |
| Recruit movement rate |                       |                                                 |
| Hyperallometry        |                       | Presence of hyperallometric fec                 |
| DD timing             |                       | Timing of density dependence                    |
| Seasonal Movement     | $\subset[TRUE,FALSE]$ | Seasonal Movement Present                       |
